The binary liquid model for gravity-driven microchannel simulations

### 2010-10-25 Text/paper.tex
Added different viscosities results. Waiting for the grid refinement, but not sure if it's needed to be included.

\section{The influence of different viscosities}
The results obtained earlier are taken for the liquiqs viscosity ratio $10$.
We performed the same simulations for the liquids viscosity ratio as $20$.
Parameters were taken as $\tau_{liquid}=4.5$ and $\tau_{bubble}=0.7$. 
{\color{red} The results showed that blah-blah-blah - I guess will be the same}.

>>>>

\section{The influence of different viscosities}
The results obtained earlier are taken for the liquiqs viscosity ratio $10$.
We performed the same simulations for the liquids viscosity ratio as $20$.
Parameters were taken as $\tau_{liquid}=4.5$ and $\tau_{bubble}=0.7$. We
haven't found significant differences with the results obtained earlier. The
comparison for the liquid thicknesses is presented on Fig.
\ref{fig:capillary:viscous}. Therefore one can validate the assumption that in
the low capillary flow regime the density ratio is not involved. As well the
gas-liquid viscosity ratio of the order $10$ is enough to obtain results
consistent with the Bretherton/Taylor problem. 
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/Capillary_Viscous/capillaries_viscous.eps}
\caption{The widths versus capillary number comparison for
$\frac{\mu_{liq}}{\mu_{gas}}=10$ and $\frac{\mu_{liq}}{\mu_{gas}}=20$. The
results show good consistency and agreement.\label{fig:capillary:viscous}}
\end{figure}
